---
title: "Group Project Notes"
author: "Amanda Chiachi"
date: "3/31/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

For our project we will be presenting the package **"Janitor"**


# Install the Following Package

**install.packages("janitor")**


# Load Libraries
```{r, message=FALSE}
library(janitor)
library(tidyverse)
library(here)
```

#available functions
clean_names()
tabyl()
remove_empty() #note we have no empty cells
get_dupes()
excel_numeric_to_date() #note we have no date data

# Notes about Package
### The main functions are:

-  clean_names() # Shane
-  tabyl() # Shane 
-  remove_empty() # Amanda 
-  get_dupes() # Ruth 
-  excel_numeric_to_date() # Kevin 

#Cleaning Data
- How to use remove_empty  
```{r}
a <- data.frame(v1 = c(7, NA, 4, NA),
                v2 = c(6, NA, 8, 7),
                v3 = c("a", NA, "b", NA), 
                v4 = c(NA, NA, NA, NA))
view(a)
a %>%
  remove_empty(c("rows", "cols"))
```
#bring in data
```{r}
here()
SGD_Samples<-read_csv("first_draft/Data/SGD_Time_Series_Samples.csv")
view(SGD_Samples)
SGD_Samples%>%
```


