---
title: "Kevin the RStudio Janitor"
author: "Kevin Candray"
date: "4/7/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading packages
```{r}
library(janitor)
library(here)
```
# Data Before the Janitor Function
| Date  | Session | Topic    |
|:------|:-------:|---------:|
| _left_ | _center_| _right_ |
|   41104| 1       | Anatomy |
|41105   |         | *Break* |
| 41106  | 2       | Tables  |
| 41107  |         | *Break* |

# Function: *excel_numeric_to_date()* 
In the event when we load data straight from excel, R tends to change the date to a series of numbers. This function decodes that for example:
```{r}
excel_numeric_to_date(41104)
excel_numeric_to_date(41105)
excel_numeric_to_date(41106)
excel_numeric_to_date(41107)
```
every set of numbers can be decoded to a certain day,

# Data After the Janitor Function
| Date     | Session | Topic    |
|:---------|:-------:|---------:|
| _left_   | _center_| _right_ |
|2012-07-14| 1       | Anatomy |
|2012-07-15|         | *Break* |
|2012-07-16| 2       | Tables  |
|2012-07-17|         | *Break* |
