---
title: "Group Project Notes"
author: "Amanda Chiachi, Kevin Candray, Shane Jordan, and Ruth Vergara Reyes"
date: "3/31/2021"
output: 
   prettydoc::html_pretty:
    theme: hpstr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

For our project we will be presenting the package **"Janitor"**


# Please Install the Following Package

**install.packages("janitor")**


# Load Libraries

```{r, message=FALSE}
library(janitor)
library(tidyverse)
library(here)
library(readxl)
library(kableExtra)
```


# Please load the following data:

This is the data that we will be using to explain the different fuctions that are going to be presented. 

```{r}
coralgrowth<-read_csv(here("first_draft/data/CoralGrowth.csv"))
view(coralgrowth) 

```


# About the Package

There are many functions in this package, but we will only be going over the top five important functions. The package helps users clean up the data, so that it can be easier to use for analysis. 

-  clean_names()     ---> Shane
-  tabyl()           ---> Shane
-  remove_empty()    ---> Amanda
-  get_dupes()       ---> Ruth
-  excel_numeric_to_date()  ----> Kevin


### clean_names()

Using the **clean_names()** function will change the format of the column names. 
  This is how the data looked before.
```{r, message=TRUE}

coralsclean<-coralgrowth[,-c(5:14)] #get rid of the analysis on Excel

coralsclean %>%
  kbl() %>%
  kable_classic()
```

  THis is the data set after

```{r}
corals<-clean_names(coralsclean)

corals %>%
  kbl() %>%
  kable_classic() 

```

### tably() 

Using the **tabyl()** function will 
```{r}
tabyl(corals, change_mg_cm2) #we can put the above object into a frequency table

# How we can use the function with a pipe
corals %>%
  tabyl(change_mg_cm2)

```


### excel_numeric_to_date()

In the event when we load data straight from excel, R tends to change the date to a series of numbers. This function decodes that for example:

## **Data Before the Janitor Function**
| Date  | Session | Topic    |
|:------|:-------:|---------:|
| _left_ | _center_| _right_ |
|   41104| 1       | Anatomy |
|41105   |         | *Break* |
| 41106  | 2       | Tables  |
| 41107  |         | *Break* |

**How we use the Function: *excel_numeric_to_date()* **

In the event when we load data straight from excel, R tends to change the date to a series of numbers. This function decodes that for example:
```{r}
excel_numeric_to_date(41104)
excel_numeric_to_date(41105)
excel_numeric_to_date(41106)
excel_numeric_to_date(41107)
```
every set of numbers can be decoded to a certain day,

## Data After the Janitor Function
| Date     | Session | Topic    |
|:---------|:-------:|---------:|
| _left_   | _center_| _right_ |
|2012-07-14| 1       | Anatomy |
|2012-07-15|         | *Break* |
|2012-07-16| 2       | Tables  |
|2012-07-17|         | *Break* |


