---
title: "Janitor Package"
author: "Amanda Chiachi, Kevin Candray, Shane Jordan, and Ruth Vergara Reyes"
date: "3/31/2021"
output: 
   prettydoc::html_pretty:
    theme: hpstr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

# Introduction

For our project we will be presenting the package called **"Janitor."**


# Please Install the Following Package

*install.packages("janitor")*


# Load Libraries

```{r, message=FALSE}
library(janitor)
library(tidyverse)
library(here)
library(readxl)
library(kableExtra)
```


# Please load the following data:

This is the data that we will be using to explain the different functions that are going to be presented. 

```{r}
coralgrowth<-read_csv(here("first_draft/data/CoralGrowth.csv"))

corals_messy <- read_csv(here("first_draft", "data", "coraldata.csv"))

```

# About the Package

There are many functions in this package that helps users clean up the data, so that it can be easier to use for data analysis and plot making. We will only be going over 5 of the most useful functons in the package.

-  clean_names()     
-  tabyl()           
-  remove_empty()
-  get_dupes()      
-  excel_numeric_to_date()


### clean_names()

Ever have a time when the names of the columns in the data that you are using are all in different formats and it just looks like a mess?
Using the ***clean_names()*** function can help you with that, because it will change all of the column names so that they all have the same format. It will change all the names into lowercase letters with a _ as a separator.  

For example, in this data set we can see that all the column names have different formats. Some use a . as a separator, others use a _ 

```{r, message=TRUE}

corals_messy%>%
  kbl() %>% # make a table in RMarkdown
  kable_classic()%>% #  Theme of the table
  kable_styling() %>% 
  scroll_box(width = "700px", height = "300px")# Table dimensions
```


To save you time and lines of code, you can just use the function     **clean_names()**. This will lead to the column names all to become lowercase and the separator is now a _

```{r}
corals<-clean_names(corals_messy) ## function we are looking at ##

corals %>%
  kbl() %>% # make a table in RMarkdown
  kable_classic()%>% # the theme of the table
    kable_styling() %>%
    scroll_box(width = "700px", height = "300px") # table dimensions 
```



### tably() 

To save you time and lines of code doing summary after summary use the **tabyl()** function. It will tell you the number of items of a value that you have, and their frequency. It essentially counts the number of times a character (you select)shows up and calculates the percentage that it makes up. The new values will show up as new columns. This function can be used in two ways... 

The first being a vector
```{r}
tabyl(corals, change_mg_cm2)%>% #we can put the object into a frequency table
  kbl() %>% # make a table in RMarkdown
  kable_classic()%>% # theme of the table
  kable_styling() %>% 
  scroll_box(width = "300px", height = "300px")# table dimensions

```

To save us some time we can do the second method, which is using it as a function within a pipe.
```{r}
corals %>%
  tabyl(change_mg_cm2)%>%  ### The pipe version ###
  kbl() %>% # make a table in RMarkdown
  kable_classic()%>% # theme of table
  kable_styling() %>%
  scroll_box(width = "300px", height = "300px")# table dimensions

```



### remove_empty()

#### Steps to follow when using *remove_empty* 

```{r}
#first make a simple data frame 
a <- data.frame(v1 = c(7, 6, 4, 5),
                v2 = c(NA, NA, NA, NA),
                v3 = c("a", "b", "c", "d"), 
                v4 = c(6, 5, 8, 10))
a %>% #data frame name
  kbl()%>% #make a table in RMarkdown
  kable_classic()%>% #classic theme
  kable_styling(full_width = FALSE, position = "left")


a_clean<-a %>% #rename data frame
  remove_empty(c("rows", "cols")) #checks for empty columns and rows, removes them!

a_clean%>%  #data frame name 
  kbl()%>% #make a table in RMarkdown
  kable_classic()%>% #classic theme
  kable_styling(full_width = FALSE, position = "left")

```

#### Usefullness on a real data set 
```{r, message=FALSE}
coralgrowth<-read_csv(here("first_draft/data/CoralGrowth.csv")) #bring in the data
coralgrowth %>% # data frame name
  kbl() %>% # make a table in RMarkdown
  kable_classic()%>%
  kable_styling() %>%
  scroll_box(width = "700px", height = "300px")# classic theme
```

What we did was remove the column **X6** due to it being all NA's. 
```{r}
coralgrowth_clean<-coralgrowth%>%  #rename data set
  remove_empty(c("rows", "cols")) #remove any rows or columns with all NAs
coralgrowth_clean %>% # data frame name
  kbl() %>% # make a table in RMarkdown
  kable_classic()%>%
  kable_styling() %>%
  scroll_box(width = "700px", height = "300px")# classic theme
```



### get_dupes()

When we want to make ensure that there are no duplicates within our data the function to use is **get_dupes()**. The function counts the amount of duplicates there are, and shows us the row that the dupicate is in. 

```{r}
corals %>%
  get_dupes("change_mg_cm2")%>%  ## the function we are using ##
  arrange(dupe_count)%>%  # arranged it by dupe count to make it organized 
  kbl() %>% # make a table in RMarkdown
  kable_classic()%>% # table theme
  kable_styling() %>%
  scroll_box(width = "700px", height = "300px")# table dimensions 
```

This can be useful in many ways. We might be able to see that we recorded the same data twice. We can look for any data changes are the same and then see if they were treated the same. Potentially, showing us that two different treatments lead to the same results. 



### excel_numeric_to_date()

In the event when we load data straight from excel, R tends to change the date to a series of numbers. This function decodes that for example:

#### **Data Before the Janitor Function**
| Date  | Session | Topic    |
|:------|:-------:|---------:|
| _left_ | _center_| _right_ |
|   41104| 1       | Anatomy |
|41105   |         | *Break* |
| 41106  | 2       | Tables  |
| 41107  |         | *Break* |

**How we use the Function: *excel_numeric_to_date()* **

In the event when we load data straight from excel, R tends to change the date to a series of numbers. This function decodes that for example:
```{r}
excel_numeric_to_date(41104)
excel_numeric_to_date(41105)
excel_numeric_to_date(41106)
excel_numeric_to_date(41107)
```
every set of numbers can be decoded to a certain day,

#### Data After the Janitor Function
| Date     | Session | Topic    |
|:---------|:-------:|---------:|
| _left_   | _center_| _right_ |
|2012-07-14| 1       | Anatomy |
|2012-07-15|         | *Break* |
|2012-07-16| 2       | Tables  |
|2012-07-17|         | *Break* |
